---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/mcmcderive.svg?branch=master)](https://travis-ci.org/poissonconsulting/mcmcderive)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/mcmcderive?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/mcmcderive)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/mcmcderive/master.svg)](https://codecov.io/github/poissonconsulting/mcmcderive?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/mcmcderive)](https://cran.r-project.org/package=mcmcderive)
<!-- badges: end -->

# mcmcderive

## Why `mcmcderive`?

`mcmcderive` is an R package to generate derived parameter(s) from Monte Carlo Markov Chain (MCMC) samples using R code.
This is useful because it means Bayesian models can be fitted without the inclusion of derived parameters which add unnecessary complexity and slow model fitting.

The `mcmc_derive()` function accepts (and returns) an [`mcmcr`](https://poissonconsulting.github.io/mcmcr/reference/mcmcr-object.html) or [`mcmcrs`](https://poissonconsulting.github.io/mcmcr/reference/mcmcrs-object.html) object.
An attempt is made to convert all other objects into 
An `mcmc.list` object can be convenrte

### Parallel Chains

If the MCMC objects have multiple chains the run time can be substantially reduced by generating the derived parameters for each chain in parallel.
In order for this to work it is necessary to:

1) Ensure plyr and foreach are installed.
2) Register a parallel backend using `foreach`.
3) Set `parallel = TRUE` in the call to `mcmc_derive()`.

A parallel backend can be registered using
```r
if (getDoParWorkers() == 1)
  registerDoParallel(4)
```

### Extras

To facilitate the translation of model code into R code the `mcmcderive` package also provides the R equivalent to common model functions such as `pow()`, `phi()` and `log() <- `.

## Demonstration

```{r}
library(mcmcderive)

mcmcr::mcmcr_example

expr <- "
  log(alpha2) <- alpha
  gamma <- sum(alpha) * sigma
"

mcmc_derive(mcmcr::mcmcr_example, expr, silent = TRUE)
```

## Installation

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
``` r
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("mcmcderive")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/mcmcderive/issues).

[Pull requests](https://github.com/poissonconsulting/mcmcderive/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms
