---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/mcmcderive.svg?branch=master)](https://travis-ci.org/poissonconsulting/mcmcderive)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/mcmcderive?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/mcmcderive)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/mcmcderive/master.svg)](https://codecov.io/github/poissonconsulting/mcmcderive?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

# mcmcderive

## Introduction

`mcmcderive` is an R package to generate derived parameters from Monte Carlo Markov Chain (MCMC) samples using R code.
The derived parameters are returned as an [`mcmcr`](https://github.com/poissonconsulting/mcmcr) object.

The `mcmcderive` package also provides the R equivalent to functions such as 

- `pow()`
- `phi()`
- `log() <- `
- `logit() <- `

that often occur in template model code.

## Demonstration

```{r}
library(mcmcderive)

mcmcr::mcmcr_example

expr <- "
  log(alpha2) <- alpha
  gamma <- sum(alpha) * sigma
"

mcmc_derive(mcmcr::mcmcr_example, expr)
```

## Installation

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
``` r
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("mcmcderive")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/mcmcderive/issues).

[Pull requests](https://github.com/poissonconsulting/mcmcderive/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.
